Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-05-27 doc/LinksToDAG.tex
minor

\begin{abstract}
Under multi-headed dependency grammar, a parse is a DAG rather than a tree.  Such formalisms can be more syntactically and semantically expressive.  However, few multi-headed corpora exist, particularly for the projective case, so it is hard to train, test, or improve such parsers.
% OLD
% investigate the benefit of such parsers or to work on making them faster or more accurate.  
To help fill this gap, we observe that link grammar already produces {\em undirected} projective graphs.  
% OLD
% ... produces parses that are similar to multi-headed projective dependency parses, except that the links are undirected. 
We use Integer Linear Programming to assign consistent directions to the labeled links in a corpus of !!! \noteJE{fill in the number} parses produced by the Link Grammar Parser, which has broad-coverage hand-written grammars of English, Russian, and other languages.  We find that such directions can indeed be consistently assigned in a way that yields valid multi-headed dependency parses. The resulting parses in English appear reasonably linguistically plausible, although they are not in general consistent with CoNLL-style parses of the same sentences; we discuss the differences.  
\end{abstract}

@@

In this paper, we are interested in relaxing the {\sc Single-Head} requirement while preserving all the others.  This means that the parse can have more than $n$ edges, allowing it to express more relationships between words.  In English, for example, here are some constructions that seem to call for a multi-headed analysis.  
\begin{description}
\item[control] In {\em ``Jill likes to skip,''} the word {\em Jill} is the subject of two verbs.  In {\em ``Jill persuaded Jack to skip,''} {\em Jack} is the object of one verb and the subject of another.  Without recognizing this, our parser would miss the syntactic invariant that {\em skip} always has a subject and {\em persuaded} always has an object.  It would also be unable to exploit the selectional preferences of both verbs to help disambiguate the parse.  This is why we prefer to make the parser aware of multi-headedness, rather than using a single-headed parser and then extracting the additional semantic roles from its output.
\item[relativization] In {\em ``The boy that Jill skipped with fell down,''} the word {\em boy} is the object of {\em with} as well as the subject of {\em fell}.  Without recognizing this, we would miss the syntactic invariant that {\em with} always has an object.  
\item[conjunction] In {\em ``Jack and Jill went up the hill,''} {\em Jack} and {\em Jill} serve as the two arguments to {\em and}, but they are also semantically subjects of {\em went}.  Without recognizing this, we would have no (local) reason for expecting the arguments of {\em and} to be nouns.
\end{description}

>>>>

\begin{abstract}
Under multi-headed dependency grammar, a parse is a DAG rather than a tree.  Such formalisms can be more syntactically and semantically expressive.  However, 
it is hard to train, test, or improve multi-headed parsers because few multi-headed corpora exist, particularly for the projective case.
% OLD
% investigate the benefit of such parsers or to work on making them faster or more accurate.  
To help fill this gap, we observe that link grammar already produces {\em undirected} projective graphs.  
% OLD
% ... produces parses that are similar to multi-headed projective dependency parses, except that the links are undirected. 
We use Integer Linear Programming to assign consistent directions to the labeled links in a corpus of 70,000 \noteJE{fill in the number} parses produced by the Link Grammar Parser, which has broad-coverage hand-written grammars of English as well as Russian and other languages.  We find that such directions can indeed be consistently assigned in a way that yields valid multi-headed dependency parses. The resulting parses in English appear reasonably linguistically plausible, although they are not in general consistent with CoNLL-style parses of the same sentences; we discuss the differences.  
\end{abstract}

@@

In this paper, we are interested in relaxing the {\sc Single-Head} requirement while preserving all the others.  This means that the parse can have more than $n$ edges, allowing it to express more relationships between words.  In English, for example, here are some constructions that seem to call for a multi-headed analysis.  
\begin{description}
\item[control] In {\em ``Jill likes to skip,''} the word {\em Jill} is the subject of two verbs.  In {\em ``Jill persuaded Jack to skip,''} {\em Jack} is the object of one verb and the subject of another.  Without recognizing this, our parser would miss the syntactic invariants that {\em skip} always has a subject and {\em persuaded} always has an object.  It would also be unable to exploit the selectional preferences of both verbs to help disambiguate the parse.  This is why we prefer to make the parser aware of multi-headedness, rather than using a single-headed parser and then extracting the additional semantic roles from its output.
\item[relativization] In {\em ``The boy that Jill skipped with fell down,''} the word {\em boy} is the object of {\em with} as well as the subject of {\em fell}.  Without recognizing this, we would miss the syntactic invariant that {\em with} always has an object.  
\item[conjunction] In {\em ``Jack and Jill went up the hill,''} {\em Jack} and {\em Jill} serve as the two arguments to {\em and}, but they are also semantically subjects of {\em went}.  Without recognizing this, we would have no (local) reason for expecting the arguments of {\em and} to be nouns.
\end{description}
